# Executive Summary

Gulf of Alaska `r species` (*Sebastes alutus*, POP) is assessed on a biennial stock assessment schedule to coincide with the availability of new trawl survey data (odd years).
In alternate (even) years we present an executive summary to recommend harvest levels for the next two years.
Please refer to last year’s full stock assessment report for further information regarding the assessment model ([Hulson et al., 2021](https://apps-afsc.fisheries.noaa.gov/refm/docs/2021/GOApop.pdf)).
A full stock assessment document with updated assessment and projection model results will be presented in next year’s SAFE report. 

We use a statistical age-structured model as the primary assessment tool for Gulf of Alaska Pacific ocean perch which qualifies as a Tier 3 stock.
For an off-cycle year, we do not re-run the assessment model, but do update the projection model with new catch information.
This incorporates the most current catch information without re-estimating model parameters and biological reference points.

## Summary of Changes in Assessment Inputs

*Changes in the input data*: There were no changes made to the assessment model inputs since this was an off-cycle year.
New data added to the projection model included an updated `r year - 1` catch and new estimated catches for `r year`-`r year + 2`.

*Changes in assessment methodology*: There were no changes in assessment methodology as this was an off-cycle year. 


## Summary of Results

New estimates for this year’s projection model are an updated `r year - 1` catch of `r catch0`, and new estimated `r year`-`r year + 2` catches of `r catch1` t, `r catch2` t, and `r catch3` t, respectively.
The `r year` catch was estimated by expanding the `r date` catch by a factor of `r exp_fac` using the last three complete catch years (`r year - 3`-`r year - 1`) to project catch through the end of the `r year` fishing year. 
To more accurately estimate future catch, an updated yield ratio of `r yld_rat` was computed using the average of the ratio of catch to ABC for the last three complete catch years (`r year - 3`-`r year - 1`).
The updated yield ratio was then multiplied against the projected ABCs for `r year + 1` and `r year + 2` from the `r year - 1` assessment model to estimate future catches. 

For the `r year + 1` fishery, we recommend the maximum allowable ABC of **`r ABC`** t from the updated projection model.
The corresponding reference values for Pacific ocean perch are summarized in the following table.
Overfishing is not occurring, the stock is not overfished, and it is not approaching an overfished condition.

The Pacific ocean perch catch/biomass ratio has ranged from less than 0.01 to 0.05 between 1991 and `r year` (Figure 9-1).
Since 2013, the catch/biomass ratio has been increasing.
This is mainly a result of the fishery fully taking the ABC in all the areas where trawling is allowed.

```{r, child= "01a-main_table.Rmd", eval = T}

```

```{r, child= "01b-apportionment.Rmd", eval = T}

```


If so are so kind as to provide tables for the plan team, place them here

```{r, child= "01c-plan_team.Rmd", eval = T}

```


