## Area Apportionment

The apportionment percentages are the same as in the `r year - 1` full assessment.
The following table shows the recommended apportionment for `r year + 1` and `r year + 2` from the random effects model. 


```{r}
# apportionment table example
appo <- vroom::vroom(here::here('partial_pop_2022', 'apportion.csv'))

flextable::flextable(appo[-1,]) %>% 
    flextable::add_header_row(values = paste0(appo[1,], "%"), top=FALSE) %>%
    flextable::border_remove() %>% 
    flextable::compose(i=1, j=1:2, part='header', 
                       value=flextable::as_paragraph('')) %>%
    flextable::compose(i=2, j=1:2, part='header', 
                        value=flextable::as_paragraph('Area Apportionment')) %>% 
    flextable::merge_h(i=1:2, part = "header") %>% 
    flextable::font(fontname = "Times New Roman", part = "all") %>%
    flextable::fontsize(size = 11, part = "all") %>% 
    flextable::align(j = 1, part = "all", align="left") %>% 
     flextable::compose(i = 1:2, j = 1, 
                       value = flextable::as_paragraph(as.character(year)), 
                       part = "body") %>% 
    flextable::compose(i = 3:4, j = 1, 
                       value = flextable::as_paragraph(as.character(year+1)), 
                       part = "body")  %>% 
    flextable::compose(i = 1:4, j = 2, 
                       value = flextable::as_paragraph(rep(c('ABC (t)', 'OFL (t)'), 2)), 
                       part = "body") %>% 
    # flextable::height(height = 0.2, part='body') %>% 
    # flextable::hrule(rule = "exact") %>% 
    flextable::hline_top(part='all') %>% 
    flextable::hline_bottom() 
  
```

Amendment 41 prohibited trawling in the Eastern area east of 140° W longitude. 
The ratio of biomass still obtainable in the W. Yakutat area (between 147° W and 140° W) is `r wyak_r`. 
This results in the following apportionment of the Eastern Gulf area:

```{r}
apportion2 <- vroom::vroom(here::here('partial_pop_2022', 'apportion2.csv'))
flextable::flextable(apportion2) %>% 
  flextable::border_remove() %>% 
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  flextable::fontsize(size = 11, part = "all") %>%
  flextable::compose(i = 1, j = 1, 
                       value = flextable::as_paragraph(as.character(year)), 
                       part = "body") %>% 
  flextable::compose(i = 2, j = 1, 
                       value = flextable::as_paragraph(as.character(year+1)), 
                       part = "body") %>% 
  flextable::compose(i = 1:2, j = 2, 
                       value = flextable::as_paragraph(rep('ABC (t)', 2)), 
                       part = "body") %>% 
  flextable::compose(j=1:2, part='header', 
                      value=flextable::as_paragraph('')) %>% 
  flextable::compose(j=3, part='header', 
                      value=flextable::as_paragraph('W. Yakutat')) %>% 
    flextable::compose(j=4, part='header', 
                      value=flextable::as_paragraph('E. Yakutat/Southeast')) %>% 
  flextable::width(j = 3, width = 1) %>% 
  flextable::width(j = 4, width = 1.5) %>% 
          flextable::hline_top(part='all') %>% 
    flextable::hline_bottom() %>% 
  flextable::align(j = 1, part = "body", align="left")
  
```
